Title of Dan's paper

### 2019-08-29 paper-figures/paper_figures.tex
done with first 7 figures

@@

@@

\begin{figure}[!hbp]
\centering
\begin{fullwidth}
\includegraphics[width=\linewidth]{5.pdf}
\end{fullwidth}
\caption{\textbf{PD and LG bursting speeds up with increasing temperature in a similar manner.} Let me know if you want me to write out the figure captions, or if you want to do it.   }
\end{figure}

@@

@@

>>>>

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Sed fringilla consequat tincidunt. Donec nec ornare leo. Nullam volutpat arcu ac placerat imperdiet. Mauris et tristique nisi. Nullam ac elit augue. Vivamus ullamcorper turpis id ipsum tincidunt, ac commodo risus lacinia. Donec ornare diam nisl, at molestie lectus commodo et. Sed scelerisque efficitur turpis, non sagittis elit pharetra vel. Sed luctus pharetra dolor, quis eleifend odio. Suspendisse lobortis nisl dui, in molestie mi consectetur sed. Aenean vitae ultricies massa. Mauris id tempor nulla. Nullam ac nisi erat. Cras congue aliquet vulputate. Nulla vel fermentum nisi. Praesent commodo, lacus at mollis luctus, arcu diam interdum tellus, nec consectetur turpis libero eget arcu.

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Sed fringilla consequat tincidunt. Donec nec ornare leo. Nullam volutpat arcu ac placerat imperdiet. Mauris et tristique nisi. Nullam ac elit augue. Vivamus ullamcorper turpis id ipsum tincidunt, ac commodo risus lacinia. Donec ornare diam nisl, at molestie lectus commodo et. Sed scelerisque efficitur turpis, non sagittis elit pharetra vel. Sed luctus pharetra dolor, quis eleifend odio. Suspendisse lobortis nisl dui, in molestie mi consectetur sed. Aenean vitae ultricies massa. Mauris id tempor nulla. Nullam ac nisi erat. Cras congue aliquet vulputate. Nulla vel fermentum nisi. Praesent commodo, lacus at mollis luctus, arcu diam interdum tellus, nec consectetur turpis libero eget arcu.

@@

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Sed fringilla consequat tincidunt. Donec nec ornare leo. Nullam volutpat arcu ac placerat imperdiet. Mauris et tristique nisi. Nullam ac elit augue. Vivamus ullamcorper turpis id ipsum tincidunt, ac commodo risus lacinia. Donec ornare diam nisl, at molestie lectus commodo et. Sed scelerisque efficitur turpis, non sagittis elit pharetra vel. Sed luctus pharetra dolor, quis eleifend odio. Suspendisse lobortis nisl dui, in molestie mi consectetur sed. Aenean vitae ultricies massa. Mauris id tempor nulla. Nullam ac nisi erat. Cras congue aliquet vulputate. Nulla vel fermentum nisi. Praesent commodo, lacus at mollis luctus, arcu diam interdum tellus, nec consectetur turpis libero eget arcu.

@@

\begin{figure}[!hbp]
\centering
\begin{fullwidth}
\includegraphics[width=\linewidth]{5.pdf}
\end{fullwidth}
\caption{\textbf{PD spike rasters triggered by LG burst starts, but not DG, exhibit regularity across temperatures.} Let me know if you want me to write out the figure captions, or if you want to do it.   }
\end{figure}

@@

\begin{figure}[!hbp]
\centering
\begin{fullwidth}
\includegraphics[width=\linewidth]{6.pdf}
\end{fullwidth}
\caption{\textbf{Phase locking of LG burst starts, but not DG, to PD cycle} Let me know if you want me to write out the figure captions, or if you want to do it.   }
\end{figure}

@@

\begin{figure}[!htp]
\centering
\begin{fullwidth}
\includegraphics[width=\linewidth]{7.pdf}
\end{fullwidth}
\caption{\textbf{LG, but not DG, bursting is phase locked to PD across temperature.} (a) Probability of LG burst starts as a function of PD phase. Each curve pools all LG burst starts in a given temperature.  (b) Probability of DG burst starts as a function of PD phase. Each curve in (a) and (b) pools all LG or DG burst starts at a given temperature. Shading indicates standard error.  (c) Mean LG start in PD phase as a function of temperature. Gray lines denote individual preparations; black line is the average of all preparations. Bars indicate standard error of the mean. (d) Probability of LG spiking as a function of PD phase. (e) Proabbility of DG spiking as a function of PD phase.  Dashed lines in all panels indicates chance level.}
\end{figure}
